Pillar 1 - Student Topic Profile

### 2019-06-05 Warning Issuance - Conformal Prediction.Rmd
create a series of scripts for warning issuance

@@

  df <- df %>% filter(significance <= significance_given)

  min(df$alpha)

@@

significance <- c(0.05, seq(0.1, 0.9, 0.1))
results <- list()
n_list <- 1

@@

Illustration of the effect of error_hat on interval's width (for significance of 99%):
```{r, fig.height=4}
Z_test %>% select(Y, Y_hat, error, error_hat, width, border_low, border_high, hit)
plot(Z_test$error, Z_test$error_hat)
```

Correlation between the actual errors and the predicted errors (error_hat):
```{r}
cor(Z_test$error, Z_test$error_hat)
```

>>>>

knitr::opts_chunk$set(cache.path = "Cache/Warning Issuance/")

@@

  df <- df %>% filter(significance >= significance_given)

  max(df$alpha) + 0.00001

@@

significance <- c(0.01, 0.05, seq(0.1, 0.9, 0.1))
results <- list()
n_list <- 1

# course <- "SSC3044"; iteration <- 1; signi <- 0.1

@@

Illustration of the effect of error_hat on interval's width (for significance of 99%):
```{r, fig.height=4, eval = F}
Z_test %>% select(Y, Y_hat, mu_hat, width, border_low, border_high, hit)
plot(Z_test$error, Z_test$mu_hat)
```

Correlation between the actual errors and the predicted errors (error_hat):
```{r, eval = F}
cor(Z_test$error, Z_test$error_hat)
```

### 2019-06-05 Warning Issuance - Grade Prediction with RF.Rmd
create a series of scripts for warning issuance

knitr::opts_chunk$set(cache.path = "Cache/Warning Issuance/")
knitr::opts_chunk$set(fig.path = "Cache/Figures/")

library(glmnet)
library(tidyverse)

load("Output/useful functions.RDATA")

@@

# Lasso

## Learn lambda with cross-validation

```{r fit_lasso, cache = TRUE} 
d_lasso <- d_lasso_course %>%
  mutate(lasso_cv = student_model %>% map(my_cv.glmnet, predictors = "GPA|Topic")) %>%
  select(-student_model)
```

## Extract results
```{r fit_lasso extract} 
d_lasso <- d_lasso %>%

  # Results from CV
  mutate(m_lasso     = lasso_cv %>% map    (~ .[["glmnet.fit"]]),
         lambda_min  = lasso_cv %>% map_dbl(~ .[["lambda.min"]]),
         lambda_1se  = lasso_cv %>% map_dbl(~ .[["lambda.1se"]]),
         index_best  = lasso_cv %>% map_dbl(~ which.min(.[["cvm"]])),
         cv_error    = list(lasso_cv, index_best) %>% pmap_dbl(~ ..1[["cvm"]][..2]),
         cv_error_sd = list(lasso_cv, index_best) %>% pmap_dbl(~ ..1[["cvsd"]][..2])) %>%

  # Best model
  mutate(intercept = list(m_lasso, index_best) %>% pmap_dbl(~ ..1[["a0"]][..2]),
         coefi     = list(m_lasso, lambda_min) %>% pmap(coef), # clearer output than pmap_dbl(~ ..1[["beta"]][,..2])
         df        = list(m_lasso, index_best) %>% pmap_dbl(~ ..1[["df"]][..2]),

         dev_null  = m_lasso %>% map_dbl(~ .[["nulldev"]]),
         dev_left  = list(m_lasso, index_best) %>% pmap_dbl(~deviance.glmnet(..1)[..2]),
         dev_expl  = dev_null - dev_left,
         dev_ratio = list(m_lasso, index_best) %>% pmap_dbl(~ ..1[["dev.ratio"]][..2])) %>%

  arrange(cv_error)
```

## Save results
```{r} 
save(d_lasso, file = "Output/lasso.RDATA")

d_lasso_app <- d_lasso %>% select(target, lasso_cv)
save(d_lasso_app, file = "APP/Recommender System/d_lasso_app.RDATA")
```

## Explore results

### CV MAE
```{r}
d_lasso %>%
  ggplot() +
  geom_histogram(aes(cv_error), bins = 14) +
  labs(x = "CV mae", caption = "red: mean\ngreen: median") +
  geom_vline(xintercept = c(mean(d_lasso$cv_error)), col = "red", alpha = 0.5) +
  geom_vline(xintercept = c(median(d_lasso$cv_error)), col = "green", alpha = 0.5)
```

meand, median and weighted mean
```{r}
mean(d_lasso$cv_error)
median(d_lasso$cv_error)
weighted.mean(d_lasso$cv_error, d_lasso$n)
```

### Predictors
Topic chosen by model are related to the course.

Show results for good (largest deviance ratio):
SCI2040 Microbiology,
SCI1004 Introduction to Chemistry,
SSC2066 Protection of Civilians in Armed Conflicts

```{r}
show_predictors <- function(course){

  coefi <- d_lasso %>% filter(target == course) %>%
    pull(coefi) %>% .[[1]] %>%
    as.matrix %>% as_tibble(rownames = "id") %>% rename(coefi = `1`)

  coefi %>% filter(id %>% str_detect("GPA")) %>% print # GPA

  coefi_topic <- coefi %>% filter(id %>% str_detect("Topic")) %>%
    filter(coefi != 0) %>%
    filter(coefi > 0 ) %>%
    top_n(3, coefi)
  print(coefi_topic) # Topic

  main_topics <- coefi_topic %>% pull(id) %>% str_replace("_", " ")

  beta %>% filter(topic %in% main_topics) %>% head(30)

}

show_predictors("SCI2040")
show_predictors("SCI1004")
show_predictors("SSC2066")
```

## Prediction

```{r my_predict} 
my_predict <- function(model, profile){

  predict.cv.glmnet(object = model, newx = profile, s = "lambda.min")

}
```

```{r} 
course_ID  <- c("COR1005", "HUM2005") # input$course
student_ID <- "6087587" # input$student

load("APP/Recommender System/student_model_nest_app.RDATA")
load("APP/Recommender System/d_lasso_app.RDATA")

student_model <- student_model_nest_app %>%

  filter(`Student ID` == student_ID) %>%

  pull(model) %>% .[[1]]

d_lasso_app %>%

  filter(target %in% course_ID) %>%

  mutate(prediction = lasso_cv %>% map_dbl(my_predict, student_model))
```

## Extra: find best alpha

Best alpha turns out to be 1 (lasso). Good, because predictor regularization also serves as predictor selection.

```{r, eval = F, cache = T} 
n_alpha <- 101
mae     <- numeric(n_alpha)
alphas  <- seq(0, 1, length.out = n_alpha)

for(i in 1 : n_alpha){

  fit_lasso <- tibble(target = course_target) %>%

    mutate(d = target %>% map(find_df),
           n = d      %>% map_dbl(nrow)) %>%

    filter(n > 20) %>%

    mutate(cv = d %>% map(my_cv.glmnet, alpha = alphas[i], predictors = "GPA|Topic")) %>%

    mutate(index_best = cv                   %>% map_dbl (~ which.min(.[["cvm"]])),
           cv_error   = list(cv, index_best) %>% pmap_dbl(~ ..1[["cvm"]][..2]    ))

  mae[i] <- weighted.mean(fit_lasso$cv_error, fit_lasso$n)

}

# slight decrease in mae as alpha increase. Set alpha = 1 in my_cv.glmnet().
m <- lm(mae ~ alphas)
plot(alphas, mae)
abline(m, col = "red")
m %>% summary
```

>>>>

knitr::opts_chunk$set(cache.path = "Cache/Warning Issuance/")
knitr::opts_chunk$set(cache.fig  = "Cache/Figures/")
load("Output/useful functions.RDATA")

library(randomForest)
library(tidyverse)

@@

# Random forest

```{r}
data(iris)

iris.rf <- randomForest(iris[,-5], iris[,5], prox=TRUE)

iris.p <- classCenter(iris[,-5], iris[,5], iris.rf$prox)

plot(iris[,3], iris[,4], pch=21, xlab=names(iris)[3], ylab=names(iris)[4],
bg=c("red", "blue", "green")[as.numeric(factor(iris$Species))],
main="Iris Data with Prototypes")

points(iris.p[,3], iris.p[,4], pch=21, cex=2, bg=c("red", "blue", "green"))
```

```{r}
rf1 <- randomForest(Species ~ ., iris, ntree=50, norm.votes=FALSE)

rf2 <- randomForest(Species ~ ., iris, ntree=50, norm.votes=FALSE)

rf3 <- randomForest(Species ~ ., iris, ntree=50, norm.votes=FALSE)

rf.all <- combine(rf1, rf2, rf3)
print(rf.all)
```

```{r}
## Look at the third trees in the forest.
getTree(randomForest(iris[,-5], iris[,5], ntree=10), 3, labelVar=TRUE)
```

```{r}
iris.rf <- randomForest(Species ~ ., iris, ntree=50, norm.votes=FALSE)
iris.rf <- grow(iris.rf, 50)
print(iris.rf)
```

```{r}
set.seed(4543)
data(mtcars)
mtcars.rf <- randomForest(mpg ~ ., data=mtcars, ntree=1000,
keep.forest=FALSE, importance=TRUE)

importance(mtcars.rf)
importance(mtcars.rf, type=1)
```

```{r}
data(imports85)
imp85 <- imports85[,-2] # Too many NAs in normalizedLosses.
imp85 <- imp85[complete.cases(imp85), ]
## Drop empty levels for factors.
imp85[] <- lapply(imp85, function(x) if (is.factor(x)) x[, drop=TRUE] else x)
stopifnot(require(randomForest))
price.rf <- randomForest(price ~ ., imp85, do.trace=10, ntree=100)
print(price.rf)
numDoors.rf <- randomForest(numOfDoors ~ ., imp85, do.trace=10, ntree=100)
print(numDoors.rf)
```

### 2019-06-05 Warning Issuance - Preparatory Course - Lasso.Rmd
create a series of scripts for warning issuance

```{r setup, include = FALSE}

knitr::opts_chunk$set(cache.path = "Cache/Warning Issuance/")
knitr::opts_chunk$set(fig.path = "Cache/Figures/")

@@

# Lasso

## Learn lambda with cross-validation

```{r fit_lasso, cache = TRUE} 
d_lasso <- d_lasso_course %>%
  mutate(lasso_cv = student_model %>% map(my_cv.glmnet, predictors = "GPA|Topic")) %>%
  select(-student_model)
```

## Extract results
```{r fit_lasso extract} 
d_lasso <- d_lasso %>%

@@

  # Best model
  mutate(intercept = list(m_lasso, index_best) %>% pmap_dbl(~ ..1[["a0"]][..2]),
         coefi     = list(m_lasso, lambda_min) %>% pmap(coef), # clearer output than pmap_dbl(~ ..1[["beta"]][,..2])
         df        = list(m_lasso, index_best) %>% pmap_dbl(~ ..1[["df"]][..2]),

@@

  arrange(cv_error)
```

## Save results
```{r} 
save(d_lasso, file = "Output/lasso.RDATA")

d_lasso_app <- d_lasso %>% select(target, lasso_cv)
save(d_lasso_app, file = "APP/Recommender System/d_lasso_app.RDATA")
```

## Explore results

### CV MAE
```{r}
d_lasso %>%
  ggplot() +
  geom_histogram(aes(cv_error), bins = 14) +
  labs(x = "CV mae", caption = "red: mean\ngreen: median") +
  geom_vline(xintercept = c(mean(d_lasso$cv_error)), col = "red", alpha = 0.5) +
  geom_vline(xintercept = c(median(d_lasso$cv_error)), col = "green", alpha = 0.5)
```

meand, median and weighted mean
```{r}
mean(d_lasso$cv_error)
median(d_lasso$cv_error)
weighted.mean(d_lasso$cv_error, d_lasso$n)
```

### Predictors
Topic chosen by model are related to the course.

Show results for good (largest deviance ratio):
SCI2040 Microbiology,
SCI1004 Introduction to Chemistry,
SSC2066 Protection of Civilians in Armed Conflicts

```{r}
show_predictors <- function(course){

  coefi <- d_lasso %>% filter(target == course) %>%
    pull(coefi) %>% .[[1]] %>%
    as.matrix %>% as_tibble(rownames = "id") %>% rename(coefi = `1`)

  coefi %>% filter(id %>% str_detect("GPA")) %>% print # GPA

  coefi_topic <- coefi %>% filter(id %>% str_detect("Topic")) %>%
    filter(coefi != 0) %>%
    filter(coefi > 0 ) %>%
    top_n(3, coefi)
  print(coefi_topic) # Topic

  main_topics <- coefi_topic %>% pull(id) %>% str_replace("_", " ")

  beta %>% filter(topic %in% main_topics) %>% head(30)

}

show_predictors("SCI2040")
show_predictors("SCI1004")
show_predictors("SSC2066")
```

## Prediction

```{r my_predict} 
my_predict <- function(model, profile){

  predict.cv.glmnet(object = model, newx = profile, s = "lambda.min")

}
```

```{r} 
course_ID  <- c("COR1005", "HUM2005") # input$course
student_ID <- "6087587" # input$student

load("APP/Recommender System/student_model_nest_app.RDATA")
load("APP/Recommender System/d_lasso_app.RDATA")

student_model <- student_model_nest_app %>%

  filter(`Student ID` == student_ID) %>%

  pull(model) %>% .[[1]]

d_lasso_app %>%

  filter(target %in% course_ID) %>%

  mutate(prediction = lasso_cv %>% map_dbl(my_predict, student_model))
```

## Extra: find best alpha

Best alpha turns out to be 1 (lasso). Good, because predictor regularization also serves as predictor selection.

```{r, eval = F, cache = T} 
n_alpha <- 101
mae     <- numeric(n_alpha)
alphas  <- seq(0, 1, length.out = n_alpha)

for(i in 1 : n_alpha){

  fit_lasso <- tibble(target = course_target) %>%

    mutate(d = target %>% map(find_df),
           n = d      %>% map_dbl(nrow)) %>%

    filter(n > 20) %>%

    mutate(cv = d %>% map(my_cv.glmnet, alpha = alphas[i], predictors = "GPA|Topic")) %>%

    mutate(index_best = cv                   %>% map_dbl (~ which.min(.[["cvm"]])),
           cv_error   = list(cv, index_best) %>% pmap_dbl(~ ..1[["cvm"]][..2]    ))

  mae[i] <- weighted.mean(fit_lasso$cv_error, fit_lasso$n)

}

# slight decrease in mae as alpha increase. Set alpha = 1 in my_cv.glmnet().
m <- lm(mae ~ alphas)
plot(alphas, mae)
abline(m, col = "red")
m %>% summary
```

>>>>

```{r setup, include = FALSE} 
knitr::opts_chunk$set(cache.path = "Cache/Warning Issuance/")
knitr::opts_chunk$set(fig.path = "Cache/Figures/")

@@

# Lasso for Preparatory courses

```{r d_lasso prep, cache = TRUE} 
d_lasso_topic <- d_lasso_course %>%
  mutate(lasso_cv = student_model %>% map(my_cv.glmnet, predictors = "Topic", alpha = 0)) %>%
  select(-student_model)
```

```{r d_lasso extract prep} 
d_lasso_topic <- d_lasso_topic %>%

@@

  # Best model
  mutate(intercept   = list(m_lasso, index_best) %>% pmap_dbl(~ ..1[["a0"]][..2]),
         coefi       = list(m_lasso, index_best) %>% pmap(~ ..1[["beta"]][,..2]),
         coefi       = coefi %>% map(~ tibble(topic = names(.), coefi = .)),
         coefi_clean = list(m_lasso, lambda_min) %>% pmap(coef),
         df        = list(m_lasso, index_best) %>% pmap_dbl(~ ..1[["df"]][..2]),

@@

  select(- m_lasso, - lasso_cv) %>%

  arrange(cv_error) %>%

  # extract coefficients
  unnest(coefi) %>%
  select(target, topic, coefi)
```

## Explore results
```{r}
d_lasso_prep <- d_lasso_topic %>%

  left_join(gamma, by = "topic") %>%
  rename(`Preparatory Courses` = document) %>%
  filter(target != `Preparatory Courses`) %>%

  # exclude 3000 (advanced) courses from preparation courses
  filter(! `Preparatory Courses` %>% str_detect("^...30")) %>%

  # double prep_score of intro courses
  mutate(is_intro = `Preparatory Courses` %>% str_detect("^...10")) %>%
  mutate(weight = coefi * (1 + is_intro)) %>%

  # prep_score
  mutate(prep_score = weight * gamma) %>%

  # aggregate prep_score
  group_by(target, `Preparatory Courses`) %>%
  summarize(prep_score = sum(prep_score)) %>%

  # identify top 15 preparation courses for each course
  group_by(target) %>%
  top_n(10, prep_score) %>%
  arrange(target, desc(prep_score))

head(d_lasso_prep, 20)
```

## Save results
```{r} 
save(d_lasso_topic, file = "Output/d_lasso_topic.RDATA")
save(d_lasso_topic, file = "APP/Recommender System/d_lasso_topic.RDATA")

save(d_lasso_prep, file = "Output/d_lasso_prep.RDATA")
save(d_lasso_prep, file = "APP/Recommender System/d_lasso_prep.RDATA")
```
